\pkg{ggenealogy}: An \proglang{R} Package for Visualizing Genealogical Data

### 2016-05-01 JSS/jss-style/article.tex
Adobe Acrobat Reader DC in caption

\documentclass[article,shortnames]{jss}
\usepackage{float}

@@

We could still improve upon Figure \ref{fig:plotCBNoText}. Even though we may be primarily interested in understanding how the path of interest is overlaid across the entire genealogical structure, we could, upon viewing the entire structure, also develop an interest in nodes that are not on the path of interest but are revealed to stand out among the rest of the genealogical structure. For instance, in Figure \ref{fig:plotCBNoText}, it may be of interest for us to determine the names of the few individuals who obtained their statistics degrees before 1900. Fortunately, within the \code{plotPathOnAll()} function, there is a variable \code{animate} that we can set to a value of TRUE to create an interactive version of the figure that allows us to hover over individual illegible labels and immediately receive their labels in a readable format.

@@

>>>>

\documentclass[article,shortnames]{jss}
\usepackage{float}
\usepackage[]{media9}

@@

We could still improve upon Figure \ref{fig:plotCBNoText}. Even though we may be primarily interested in understanding how the path of interest is overlaid across the entire genealogical structure, we could, upon viewing the entire structure, also develop an interest in nodes that are not on the path of interest but are revealed to stand out among the rest of the genealogical structure. For instance, in Figure \ref{fig:plotCBNoText}, it may be of interest for us to determine the names of the few individuals who obtained their statistics degrees before 1900. Fortunately, within the \code{plotPathOnAll()} function, there is a variable \code{animate} that we can set to a value of TRUE to create an interactive version of the figure that allows us to hover over individual illegible labels and immediately receive their labels in a readable format. A short video demonstration of these interactive features can be viewed upon clicking on Figure \ref{fig:plotAnimate}.

@@

\begin{figure}[H]
    \centering
    \includemedia[width=1.0\textwidth, addresource=animateGen.mov, deactivate=onclick, flashvars={source=animateGen.mov}]{\includegraphics{./plotCBNoText.png}}{VPlayer.swf}
    \caption{Upon clicking on this figure twice, a short video demonstrating the animation features for this function can be viewed. Please note that to properly view this video, the PDF version of this paper must be opened in Adobe Acrobat Reader DC, which can be downloaded free of charge.}
    \label{fig:plotAnimate}
\end{figure}
